Between Subgraph Isomorphism and Maximum Common Subgraph

### 2017-02-01 poster/poster.tex
heading size, vspace round figure

\renewcommand{\Huge}{\fontsize{77.2}{96}\selectfont}

@@

The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to
a subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.

@@

Are there instances for which $k = 0$ is unsatisfiable, but that
are satisfiable for small $k$? For the problem families which
do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.

\begin{center}
\input{gen-graph-which-k-by-family}
\end{center}

In the ``phase'' family, which consists of instances
crafted to be extremely difficult to solve, we are not able
to answer this question, and in the ``scalefree'' family we
see no satisfiable instances with low but not zero $k$.

@@

\begin{wrapfigure}[11]{r}{0.66\linewidth}
\begin{center}
\input{gen-graph-runtimes}
\end{center}
\end{wrapfigure}
What would happen if we used the $k$-less approach to solve the
maximum common induced problem? We could simply start
at $k = 0$, and increase $k$ until a solution is found. This \textbf{tackles the problem in the opposite direction to existing
approaches}, which work by attempting to construct
larger and larger solutions. In the figure, ``$k\downarrow$'' is our algorithm, whilst ``FC'' and
``clique'' are state of the art maximum common subgraph algorithms.

@@

We see that \textbf{our approach is able to close over twice
as many of these instances as the previous state of the art}---which struggles due to its RAM requirements.
On instances designed for the maximum subgraph problem we are still the \newline single strongest solver.
}
\begin{columns}
\column{0.5}

@@

\block{Future Work}{
    \begin{itemize}
        \item ~ Develop an algorithm for maximum common subgraph which makes use of an upper bound from our approach and a lower bound from the clique approach, stopping when the bounds converge.
    \end{itemize}
}

@@

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=-0.5cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.reilly.2@research.gla.ac.uk}}
    }
}

>>>>

\renewcommand{\Huge}{\fontsize{96}{124}\selectfont}

@@

The \textbf{maximum common subgraph problem} is to find the largest graph which is isomorphic to  subgraph of two graphs simultaneously---the size of the maximum common subgraph gives us a measure of how similar two graphs are.

@@

Are there instances for which $k = 0$ is unsatisfiable, but that
are satisfiable for small $k$? For the problem families which
do not consist entirely of satisfiable instances, we plot this for both the induced and non-induced variants.
\vspace*{1.48cm}
\bigskip
\begin{center}
\input{gen-graph-which-k-by-family}
\end{center}
\bigskip
\vspace*{1.46cm}
In the ``phase'' family, which consists of instances
crafted to be extremely difficult to solve, we are not able
to answer this question, and in the ``scalefree'' family we
see no satisfiable instances with low but not zero $k$.

@@

\begin{wrapfigure}[13]{r}{0.66\linewidth}
\begin{center}
\input{gen-graph-runtimes}
\end{center}
\end{wrapfigure}
What would happen if we used the $k$-less approach to solve the
maximum common induced problem? We could simply start
at $k = 0$, and increase $k$ until a solution is found. This \textbf{tackles the problem in the opposite direction to existing
approaches}, which work by attempting to construct
larger and larger solutions. In the figure, ``$k\downarrow$'' is our algorithm, whilst ``FC'' and
``clique'' are state of the art maximum common subgraph algorithms.

@@

We see that \textbf{our approach is able to close over twice
as many of these instances as the previous state of the art}---which struggles due to its RAM requirements.
On instances designed for the maximum subgraph problem we are still the single strongest solvers, and our performance tends to be complementary to that of the clique encoding.
}
\begin{columns}
\column{0.5}

@@

\block{Future Work}{
Develop an algorithm for maximum common subgraph which makes use of an upper bound from our approach and a lower bound from the clique approach, stopping when the bounds converge.
}

@@

{
    \colorlet{blockbodybgcolor}{uofgsandstone!80!white}
    \colorlet{blocktitlebgcolor}{uofgsandstone!80!white}
    \block[bodyverticalshift=1.2cm]{}{
        This work was supported by the Engineering and Physical Sciences Research Council [grant
        numbers EP/K503058/1 and EP/M506539/1]. \hfill \texttt{\textcolor{white}{c.reilly.2@research.gla.ac.uk}}
    }
}
